Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-22 ms.qmd
Added some code to avoid summary of predcitions. This way I have the whole PD to work with in the global future climate predcitions

@@

@@

@@

# Now that we have all the predictions we can merge the data together. Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect. So we'll remove it. While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data. Note there are only 134 species because this is subset of the wild data.
  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
  spp_wild  <- length(unique(sub_data$spp))
```

>>>>

  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
  terre_pred_no_sum <- cbind(new_data_t2, t(predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))

@@

  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
  marine_pred_no_sum <- cbind(new_data_m, t(predict(model5_bayes, newdata = new_data_m, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))

@@

  # We'll also keep the whole postriopr which we'll use later on. We need to transpose so that the data match. Each numbered columns is one sample of the posterior.
  fresh_pred_non_sum <- cbind(new_data_f, t(predict(model5_bayes, newdata = new_data_f, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty")))

@@

# Now that we have all the predictions we can merge the data together. Note that species itself is not really that useful because each prediction at each latitude and longitude should incoperate the species effect. So we'll remove it. While I retain spp, it's still not totally specific to the species, but left it there so it's clear how these data match with the wild data. Note there are only 134 species because this is subset of the wild data.
  all_pred <- rbind(terrest_data, marine_data, fresh_data) %>% dplyr::select(-species_full)
  all_pred_no_sum <- rbind(terre_pred_no_sum, marine_pred_no_sum, fresh_pred_non_sum) %>% dplyr::select(-species_full)
  spp_wild  <- length(unique(sub_data$spp))
```
